---
title: "p8105_hw6_zh2494"
author: "zhuolun"
date: "11/29/2021"
output: github_document
---

```{r}
library(tidyverse)
library(viridis)
library(modelr)
library(mgcv)
library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
set.seed(1)
```

# Problem 1

read and clean the data  
* The column names are tidy so no need to do anything  
* Convert units: (pounds to grams, inches to centimeters)  
```{r}
baby_df = 
  read_csv("data/birthweight.csv") %>% 
  mutate(
    babysex = factor(babysex),
    frace = factor(frace),
    malform = factor(malform),
    mrace = factor(mrace),
    mheight = mheight * 2.54,
    delwt = delwt * 453.592,
    ppwt = ppwt * 453.592,
    wtgain = wtgain * 453.592)
    
```

* checks the number of na, there is 0 missing value.  
```{r}
sum(is.na(baby_df))
```

Create models 
```{r}
model_len_ges = lm(bwt ~ blength + gaweeks, data = baby_df)
model_len_ges %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

model_head_len_sex = lm(bwt ~ bhead * blength * babysex, data = baby_df)
model_head_len_sex %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

The p-value = 0 becasue it is smaller than the minimum display value. Also notice that `bhead:blength` is not significant.  

the plot of model residuals against fitted values for the first model: length at birth and gestational age as predictors   

```{r}
baby_df %>% 
  modelr::add_residuals(model_len_ges) %>% 
  modelr::add_predictions(model_len_ges) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()
```
comment: there are some wired values, but overall is good  

a plot of model residuals against fitted values for the second model: head circumference, length at birth, sex, and all interactions (including the three-way interaction).  

```{r}
baby_df %>% 
  modelr::add_residuals(model_head_len_sex) %>% 
  modelr::add_predictions(model_head_len_sex) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()

```
comment: there are some wired values, but overall is good 

Both required models are good. Now consider my own models.  

```{r}
mymodel =
  lm(bwt ~ (bhead + blength + delwt + mheight + pnumlbw + ppbmi + ppwt + smoken + wtgain)^2, data = baby_df)

baby_df %>% 
  modelr::add_residuals(mymodel) %>% 
  modelr::add_predictions(mymodel) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point()
```

```{r}
mod_select = step(mymodel, direction = 'backward')
```

```{r}
mymodel2 = lm(bwt ~ bhead + blength + delwt + mheight + ppbmi + ppwt + smoken + 
    wtgain + bhead:mheight + bhead:ppbmi + bhead:smoken + blength:delwt + 
    blength:mheight + blength:ppbmi + blength:smoken + delwt:ppbmi + 
    delwt:wtgain + mheight:ppbmi + mheight:ppwt + ppwt:wtgain, data = baby_df)
baby_df %>% 
  modelr::add_residuals(mymodel2) %>% 
  modelr::add_predictions(mymodel2) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point()
```

```{r}
mod_df = 
  baby_df %>% 
  select(bwt, blength, gaweeks, bhead, babysex, delwt, mheight, pnumlbw, ppbmi, ppwt, smoken, wtgain)

cv_mod = 
  crossv_mc(mod_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_mod = 
  cv_mod %>% 
  mutate(
    mod_len_ges  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod_head_len_sex = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x)),
    mod_mine = map(train, ~lm(bwt ~ bhead + blength + delwt + mheight + ppbmi + ppwt + smoken + 
    wtgain + bhead:mheight + bhead:ppbmi + bhead:smoken + blength:delwt + 
    blength:mheight + blength:ppbmi + blength:smoken + delwt:ppbmi + 
    delwt:wtgain + mheight:ppbmi + mheight:ppwt + ppwt:wtgain, data = .x))) %>% 
  mutate(
    rmse_len_ges = map2_dbl(mod_len_ges, test, ~rmse(model = .x, data = .y)),
    rmse_head_len_sex = map2_dbl(mod_head_len_sex, test, ~rmse(model = .x, data = .y)),
    rmse_mine = map2_dbl(mod_mine, test, ~rmse(model = .x, data = .y)))
```

Plot the prediction error distribution for each model.

```{r}
cv_mod %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin()
```

the head_len_sex and mine models are better than len_ges model. mine model is little bit better than head_len_sex model, though there is a little overlap between them. 


# problem 2
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Do a simple linear regression with `tmax` as the response and `tmin` as the predictor.  
use `bootstrap` to generate 5000 samples;  
fit the linear regression;  
extract `r.squared` and `log_b1b2` value of each sample


```{r}
simple_df = 
  weather_df %>%
  select(tmax, tmin)
```

```{r}
simple_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point() +
  stat_smooth(method = "lm")
```

```{r}
bootstrap_df =
  simple_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)),
    result1 = map(models, broom::glance),
    result2 = map(models, broom::tidy)
  ) %>% 
  select(-strap, -models) %>% 
  unnest(result1, result2) %>% 
  select(.id, term, estimate, r.squared) %>% 
  group_by(.id) %>% 
  mutate(
    log_b1b2 = log10(prod(estimate))
  ) %>% 
  ungroup
```

confidence interval for 2.5% and 97.5% quantiles to provide a 95% CI.  
```{r}
bootstrap_df %>% 
  group_by(term) %>% 
  summarize(
    rsqr_ci_lower = quantile(r.squared, 0.025),
    rsqr_ci_higher = quantile(r.squared, 0.975),
    log_ci_lower = quantile(log_b1b2, 0.025),
    log_ci_higher = quantile(log_b1b2, 0.975),
  )
```

plot the distribution of estimate for `r.squared`.      
```{r}
bootstrap_df %>% 
  filter(term == "tmin") %>% 
  ggplot(aes(x = r.squared)) + 
  geom_density()
```
comment: the distribution of `r.squared` looks like normal, but it skewed a little bit to the left. Besides, the shape is a little thin.  

plot the distribution of estimate for `log_b1b2`. 
```{r}
bootstrap_df %>% 
  filter(term == "tmin") %>% 
  ggplot(aes(x = log_b1b2)) + 
  geom_density()
```
comment: the distribution of `log_b1b2` looks like normal, but it skewed a little bit to the left. The shape is a little thin as well.  
